---
title: "Some Days without Cafeine"
author: "Radoslav Tsvetkov"
date: "2022-07-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Try to see the influecne of Caffeine on my Sleep

### Here are the data

```{r , echo=FALSE, warning=FALSE, message=FALSE}
caf <- read.csv("oura.csv")
caf$Caf <- as.factor(ifelse(caf$Caffeine == 0, "No", "Yes"))
library(dplyr)
grpDat <- group_by(caf, Caf)
sum.tab <- summarize(grpDat, 
          mean.Deep.Sleep = mean(Deep.Sleep.Dur),
          mean.Total.Sleep = mean(Total.Sleep.Dur),
          meanLoRHR = mean(Lo.RHR),
          mean.AvHRV = mean(Avg.HRV),
          mean.Restless.Sleep = mean(Restless.Sleep))
library(kableExtra)
sum.tab %>%
  kbl() %>%
  kable_paper(full_width = F)   %>% 
  kable_styling()


summary(caf$Total.Sleep.Dur/3600)
summary(caf$Deep.Sleep.Dur/3600)
par(mfrow = c(1, 2))
hist(caf$Deep.Sleep.Dur, breaks = 5)
hist(caf$Total.Sleep.Dur)
```

### Visualise the Data
```{r , echo=FALSE, warning=FALSE, message=FALSE}
par(mfrow = c(2, 2))
boxplot(Deep.Sleep.Dur ~ Caf, data = caf)
stripchart(Deep.Sleep.Dur ~ Caf, data = caf, method = "jitter", vertical = TRUE,
           pch = 19, add = TRUE)

boxplot(Total.Sleep.Dur ~ Caf, data = caf)
stripchart(Total.Sleep.Dur ~ Caf, data = caf, method = "jitter", vertical = TRUE,
           pch = 19, add = TRUE)


boxplot(Restfulness.Score ~ Caf, data = caf)
stripchart(Restfulness.Score ~ Caf, data = caf, method = "jitter", vertical = TRUE,
           pch = 19, add = TRUE)


boxplot(Avg.HRV ~ Caf, data = caf)
stripchart(Avg.HRV ~ Caf, data = caf, method = "jitter", vertical = TRUE,
           pch = 19, add = TRUE)

par(mfrow = c(1, 1))
```

## Influence on Deep Sleep Duration

```{r , echo=FALSE, warning=FALSE, message=FALSE}
caf$DeepSleep.Stat <-as.factor(ifelse(caf$Deep.Sleep.Dur > mean(caf$Deep.Sleep.Dur), "more", "less"))
tab.Deep.Sleep <- table(caf$Caf, caf$DeepSleep.Stat)
names(dimnames(tab.Deep.Sleep)) <- c("Cafeine", "Deep Sleep")

library(knitr)
kable(tab.Deep.Sleep, caption = "Deep Sleep Deviation", format = "html", table.attr = "style='width:30%;'")

```

# Let's try fisher tests to see if there's a diffeence

* H0: The two variables are independent.
* H1: The two variables relate to each other.


```{r , echo=FALSE, warning=FALSE, message=FALSE}
fisher.test(tab.Deep.Sleep)
```
*We can NOT reject H0 - the variables might be independent*



## Influence Total Sleep Duration
```{r , echo=FALSE, warning=FALSE, message=FALSE}
caf$TotSleep.Stat <-as.factor(ifelse(caf$Total.Sleep.Dur > mean(caf$Total.Sleep.Dur), "more", "less"))
tab.Tot.Sleep <- table(caf$Caf, caf$TotSleep.Stat)
names(dimnames(tab.Tot.Sleep)) <- c("Cafeine", "Tot Sleep ")

tab.Tot.Sleep %>%
  kbl() %>%
  kable_paper(full_width = F)   %>% 
  kable_styling()
```

### Let's try fisher test for the Total Sleep

* H0: The two variables are independent.
* H1: The two variables relate to each other.

```{r , echo=FALSE, warning=FALSE, message=FALSE}
fisher.test(tab.Tot.Sleep)
```
*We can NOT reject H0 - the variables might be independent*

## Influence on the Sleep Resfullness 
```{r , echo=FALSE, warning=FALSE, message=FALSE}
caf$Rest.Stat <-as.factor(ifelse(caf$Restfulness.Score > mean(caf$Restfulness.Score), "more", "less"))
tab.Restlessness <- table(caf$Caf, caf$Rest.Stat)
names(dimnames(tab.Restlessness)) <- c("Cafeine", "Restfulness.Score")
tab.Restlessness

tab.Restlessness %>%
  kbl() %>%
  kable_paper(full_width = F)   %>% 
  kable_styling()
```

### Let's try fisher test for the Total Sleep

* H0: The two variables are independent.
* H1: The two variables relate to each other.

```{r , echo=FALSE, warning=FALSE, message=FALSE}
fisher.test(tab.Restlessness)
```
*We can NOT reject H0 - the variables might be independent*